\documentclass{article}


\begin{document}

	\section{Description}
	Dots and Boxes is a game for two players.Starting with an empty grid of dots,
        two players take turns adding a single horizontal or vertical line between two 
        unjoined adjacent dots. The player who completes the fourth side of a 1x1 box 
        (or groups of one or more adjacent boxes) earns one point and takes another turn.
	
	\section{Features}
        There are options for the type of the game "beginner , expert and playing vs computer" 
	There are undo and redo options for the player for one move.
        Player can stop and save the game at any time and can continue this game at any time after that.
        There is a list of TOP 10 WINNERS.
	
	\section{Design Overview}
	
	
	\section{Assumptions}
	User will not press button "s" or "z" by mistake.
	When user overwrite a saved file He can't be back in his step.
        
	\section{Data Structure}
		\subsection{WINDOW struct}
		
		\subsection{2D array for the internal representation of the grid}
		
		\subsection{inGameData struct}
		
		\subsection{player struct}
		
		\subsetion{
	
	
	\section{Most Important Modules}
	
	
	\section{Pseudocode}
	
	
	\section{User Manual}
         When user opens the game,He will choose start game from the menu by pressing "enter" then choose mode ,for example "beginner vs beginner" 
         then the suitable grid will appear.He will choose his first two point to draw a line between them ,then the second player must choose his
         two points too to draw his lines and so on until one of the two players win.   
	
	\section{Sample Runs}
	
	
	\section{References}
		\subsection{For the user interface:}
			#links?
			https://github.com/wmcbrine/PDCurses/blob/master/docs/
			https://coderecap.com/pdcurses-getting-started-lesson-1/
			
			https://invisible-island.net/ncurses/ncurses-intro.html#introduction (ncurses not pdcurses)
			http://www.tldp.org/HOWTO/NCURSES-Programming-HOWTO/intro.html (ncurses not pdcurses)
		\subsection{For the grid internal representation}
			http://theoryofprogramming.com/2014/12/24/graph-theory-basics/
			https://www.geeksforgeeks.org/graph-and-its-representations/
			https://www.geeksforgeeks.org/graph-data-structure-and-algorithms/

////////////////////////////////////////////////////////////////////////////////////////////////
			
	                https://www.geeksforgeeks.org/strtok-strtok_r-functions-c-examples/
                        https://www.tutorialspoint.com/c_standard_library/c_function_strtok.htm
	                https://www.tutorialspoint.com/c_standard_library/c_function_atoi.htm
                        https://www.programiz.com/c-programming/c-file-input-output
                        https://www.geeksforgeeks.org/rand-and-srand-in-ccpp/
	                


\end{document}